

```{r echo= FALSE, message = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(tidyverse)
library(gridExtra)

## Convert to long format for p1 and p3 plots
dataWide = alldata %>% 
  filter(state == tabstate) %>%
  mutate(Date = as.Date(date,format = "%m/%d/%y"),
         Date = factor(str_remove(Date,"2020-")),
         Currently.sick = positive - recovered,            
         New.cases = as.integer(positiveIncrease),
         Daily.tests = totalTestResultsIncrease,
         Daily.tests = ifelse((Daily.tests == 66 & tabstate == "Minnesota"), 367, Daily.tests),   # Known bad datapoint for MN in data set, forcing it to fit
         PositivePercent = positiveIncrease / Daily.tests,
         ICUPercent = inIcuCumulative / positive,
         HospitalizedPercent = hospitalized / positive
         ) %>%
  select(Date = Date, 
         Total.cases = positive,
         Total.tested = totalTestResults,
         Currently.hospitalized = hospitalizedCurrently,
         ICU = inIcuCumulative,
         Total.deaths = death,
         Total.recovered = recovered,
         Daily.tests = Daily.tests,            
         New.cases = New.cases,              
         Currently.sick = Currently.sick,        
         New.deaths = deathIncrease,             
         New.ICU = inIcuCurrently,                
         New.hospitalized = hospitalizedIncrease,       
         New.sick = positiveIncrease,               
         PositivePercent = PositivePercent,
         ICUPercent = ICUPercent,            
         HospitalizedPercent = HospitalizedPercent)




dataLongDailyTests <- dataWide %>% 
  pivot_longer(c(-Date, -Daily.tests), names_to = "Variable", values_to = "Value")

## get data for most recent date 
dataWidePlain <- dataWide %>% 
  filter(Date == last(Date))
  
SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything())

Bar_Close <- if_else(is.na(SO %>% filter(name == "Bar_Close") %>%  pull(value)), "None", SO %>% filter(name == "Bar_Close") %>%  pull(value))
School_Close <- if_else(is.na(SO %>% filter(name == "School_Close") %>%  pull(value)), "None", SO %>% filter(name == "School_Close") %>%  pull(value))
StayHomeOrder <- if_else(is.na(SO %>% filter(name == "StayHomeOrder") %>%  pull(value)), "None", SO %>% filter(name == "StayHomeOrder") %>%  pull(value))

```

## `r renderText(tabstate)` COVID-19 Summary 
#### (`r format(Sys.time(), "%Y-%m-%d")`)

* Testing
  + Total number of completed tests: **`r prettyNum(dataWidePlain$Total.tested, big.mark=",")`** (up `r (dataWidePlain$Daily.tests)`)
  + Total positive: **`r (dataWidePlain$Total.cases)`** (up `r (dataWidePlain$New.cases)`)
* Case info   
  + Patients who are currently sick: **`r (dataWidePlain$Currently.sick)`** (`r (ifelse(dataWidePlain$New.sick <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.sick)))`)
+ Total deaths: **`r (dataWidePlain$Total.deaths)`** (`r (ifelse(dataWidePlain$New.deaths <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.deaths)))`)
  - Hospitalization   
  - Hospitalized as of today: **`r (dataWidePlain$Currently.hospitalized)`** (up `r (dataWidePlain$New.hospitalized)`)
  - Hospitalized in ICU as of today: **`r (dataWidePlain$ICU)`** (`r (ifelse(dataWidePlain$New.ICU <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.ICU)))`)
* Govvenor Orders
  - Resturant and Bar Closures: **`r Bar_Close`**
  - School Closures: **`r School_Close`**
  - Stay Home Orders: **`r StayHomeOrder`**

```{r plot1, echo=FALSE, warning = FALSE, message=FALSE}

## plots from COVID.R
df <- dataLongDailyTests %>% 
  drop_na(Daily.tests) %>% 
  filter(Variable %in% c("New.deaths","New.cases"))

loclevels <- droplevels(df$Date)

SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything())

loc = dataLongDailyTests %>%
  drop_na(Daily.tests) %>%
  distinct(Date) %>%
  mutate(Loc = as.integer(factor(Date))) %>%
  filter(Date %in% SO$value) %>%
  pull(Loc)



p1 <- ggplot(df, aes(Date, Value, fill = Variable, label = Value)) +
  geom_col(position = "identity") +
  geom_text(data = dataLongDailyTests %>% 
              drop_na(Daily.tests) %>% 
              filter(Variable %in% c("New.deaths")) %>% 
              filter(Value > 0), aes(x = Date, y = Value), nudge_y = 1) +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(size = 11, 
                                   angle = 90, 
                                   hjust = 1), 
        text = element_text(size = 14), 
        legend.text = element_text(size = 12)) +
  labs(y = "Number of new cases", 
       title = "MN COVID-19: daily new cases and deaths", 
       fill = "") +
  geom_vline(xintercept = loc, lty = 2) + 
  annotate("label", 
           x = SO$value ,
           y = c(max(df$Value) * 0.50, max(df$Value) * 0.40, max(df$Value) * 0.50), 
           label = SO$name) +
  scale_fill_brewer(name = "", palette = "Set2", labels = c("New case", "New death"))

renderPlot({
  p1
  })

```


```{r plot2, echo=FALSE, warning = FALSE, message=FALSE}

## plots from COVID.R
df <- dataWide %>% 
  drop_na(Daily.tests)

loclevels <- droplevels(df$Date)

SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything())

loc = dataLongDailyTests %>%
  drop_na(Daily.tests) %>%
  distinct(Date) %>%
  mutate(Loc = as.integer(factor(Date))) %>%
  filter(Date %in% SO$value) %>%
  pull(Loc)

df <- df %>%
  select(Date, PositivePercent, Daily.tests, Date, Daily.tests) 

df$PositivePercent[which(!is.finite(df$PositivePercent))] <- 0

p2 <- ggplot(df, aes(x = Date, y = PositivePercent * 100, size = Daily.tests, label = Date, fill = Daily.tests)) +
  geom_line(aes(group = 1), size = 1, color = "gray20") +
  geom_point(shape = 21, stroke = 1.5) +
  labs(x = "Date", y = "Percentage (%)", 
       title = "MN COVID-19: daily positive case percentage", 
       size = "Number of daily tests", 
       fill = "Number of daily tests") +
  theme(legend.position = "bottom", 
        axis.text.x = element_text(size = 11, 
                                   angle = 90, 
                                   hjust = 1), 
        text = element_text(size = 14),
        legend.text = element_text(size = 12)) +
  geom_vline(xintercept = loc, lty = 2) + 
  annotate("label", 
           x = SO$value,
           #y = c(12, 15, 15), 
           y = c(max(df$PositivePercent)* 100 * 0.75, max(df$PositivePercent)* 100 * 0.65, max(df$PositivePercent)* 100 * 0.75),
           label = SO$name) +
  guides(fill = guide_legend(), 
         size = guide_legend())  +
  scale_fill_gradient(low = "yellow", 
                      high = "red", 
                      na.value = NA) +
  guides(fill = guide_legend(nrow = 2,byrow = TRUE))


renderPlot({
  p2
  })

```

