

```{r echo= FALSE, message = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(RcppRoll)
library(lubridate)
library(ggrepel)

## Convert to long format for p1 and p3 plots
dataWide = alldata %>% 
  filter(state == tabstate) %>%
  mutate(Date = as.Date(date,format = "%m/%d/%y"),
         #Datef = factor(str_remove(Date,"2020-")),
         Currently.sick = positive - recovered,            
         New.cases = as.integer(positiveIncrease),
         Daily.tests = totalTestResultsIncrease,
         Daily.tests = ifelse((Daily.tests == 66 & tabstate == "Minnesota"), 367, Daily.tests),   # Known bad datapoint for MN in data set, forcing it to fit
         PositivePercent = positiveIncrease / Daily.tests,
         DeathPercent = death / positive,
         ICUPercent = inIcuCumulative / positive,
         HospitalizedPercent = hospitalized / positive
         ) %>%
  select(Date = Date, 
         Total.cases = positive,
         Total.tested = totalTestResults,
         Currently.hospitalized = hospitalizedCurrently,
         ICU = inIcuCumulative,
         Total.deaths = death,
         Total.recovered = recovered,
         Daily.tests = Daily.tests,            
         New.cases = New.cases,              
         Currently.sick = Currently.sick,        
         New.deaths = deathIncrease,             
         New.ICU = inIcuCurrently,                
         New.hospitalized = hospitalizedIncrease,       
         New.sick = positiveIncrease,               
         PositivePercent = PositivePercent,
         DeathPercent = DeathPercent,
         ICUPercent = ICUPercent,            
         HospitalizedPercent = HospitalizedPercent)




dataLongDailyTests <- dataWide %>% 
  pivot_longer(c(-Date, -Daily.tests), names_to = "Variable", values_to = "Value")

## Long data for New cases and deaths with n day moving average
# set number of days for moving average 
moveAvg = 5
dataLongAvg = dataLongDailyTests %>%
  group_by(Variable) %>%
  mutate(movAvgValue = RcppRoll::roll_mean(Value, moveAvg, fill = "left", align = "right"))

## get data for most recent date 
dataWidePlain <- dataWide %>% 
  filter(Date == last(Date))
  
SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything())

Bar_Close <- if_else(is.na(SO %>% filter(name == "Bar_Close") %>%  pull(value)), "None", SO %>% filter(name == "Bar_Close") %>%  pull(value))
School_Close <- if_else(is.na(SO %>% filter(name == "School_Close") %>%  pull(value)), "None", SO %>% filter(name == "School_Close") %>%  pull(value))
StayHomeOrder <- if_else(is.na(SO %>% filter(name == "StayHomeOrder") %>%  pull(value)), "None", SO %>% filter(name == "StayHomeOrder") %>%  pull(value))
CurbsidePickup <- if_else(is.na(SO %>% filter(name == "CurbsidePickup") %>%  pull(value)), "None", SO %>% filter(name == "CurbsidePickup") %>%  pull(value))
StaySafeOrder <- if_else(is.na(SO %>% filter(name == "StaySafeOrder") %>%  pull(value)), "None", SO %>% filter(name == "StaySafeOrder") %>%  pull(value))


```

## `r renderText(tabstate)` COVID-19 Summary 
#### (`r format(Sys.time(), "%Y-%m-%d")`)

* Testing
  + Total number of completed tests: **`r prettyNum(dataWidePlain$Total.tested, big.mark=",")`** (up `r (dataWidePlain$Daily.tests)`)
  + Total positive: **`r (dataWidePlain$Total.cases)`** (up `r (dataWidePlain$New.cases)`)
* Case info   
  + Patients who are currently sick: **`r (dataWidePlain$Currently.sick)`** (`r (ifelse(dataWidePlain$New.sick <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.sick)))`)
+ Total deaths: **`r (dataWidePlain$Total.deaths)`** (`r (ifelse(dataWidePlain$New.deaths <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.deaths)))`)
  - Hospitalization   
  - Hospitalized as of today: **`r (dataWidePlain$Currently.hospitalized)`** (up `r (dataWidePlain$New.hospitalized)`)
  - Hospitalized in ICU as of today: **`r (dataWidePlain$ICU)`** (`r (ifelse(dataWidePlain$New.ICU <0, sprintf("down"), sprintf("up")))` `r (abs((dataWidePlain$New.ICU)))`)
* Govvenor Orders
  - Resturant and Bar Closures: **`r Bar_Close`**
  - School Closures: **`r School_Close`**
  - Stay Home Orders: **`r StayHomeOrder`**
  - Curbside Pickup: **`r CurbsidePickup`**
  - Stay Safe Order: **`r StaySafeOrder`**


```{r plot1, echo=FALSE, warning = FALSE, message=FALSE}

## plots from COVID.R
df <- dataLongAvg %>% 
  drop_na(Daily.tests) %>% 
  filter(Variable %in% c("New.deaths","New.cases"))

SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything()) %>%
  mutate(value = as.Date(value, "%m - %d - %Y"))

ymax <- max(df$Value) * 1.25

p1 <- ggplot(df, aes(Date, Value, fill = Variable, label = Value)) +
  geom_col(position = "dodge", alpha = .5, width = .85) +
  labs(y = "Number of new cases", 
       title = "MN COVID-19: daily new cases and deaths", 
       fill = "") +
  geom_vline(xintercept = SO$value, lty = 2) + 
  geom_path(data = dataLongAvg %>% filter(Variable %in% c("New.deaths","New.cases")), aes(Date, movAvgValue, color = Variable, group = Variable), size = 1.6, alpha = .9) +
  #geom_text_repel(data = dataLongDailyTests %>% 
  #                  filter(Variable %in% c("New.cases")) %>% 
  #                  filter(Date == last(Date)), aes(x = Date, y = Value), 
  #                segment.color = NA, direction = "y", box.padding = .05, nudge_x = -.25, nudge_y = 1, size = 4) +
  #geom_text_repel(data = dataLongDailyTests %>% 
  #                  filter(Variable %in% c("New.deaths")) %>% 
  #                  filter(Date == last(Date)), aes(x = Date, y = Value), 
  #                segment.color = NA, direction = "y", box.padding = .05, nudge_x = .25, nudge_y = 1, size = 4, ylim = c(0, Inf)) +
  ylim(0, ymax) +
  annotate("label", 
           x = SO$value ,
           y = c(ymax * 0.30, ymax * 0.50, ymax * 0.70, ymax * 0.85, ymax * 0.95), 
           label = SO$name) +
   annotate("rect", 
            xmin = as.Date(today(), format = '%d-%B-%Y') - 7, 
            xmax = today(), 
            ymin = 0, 
            ymax = Inf, 
            alpha = .15) +
  labs(x = "", y = "Number of new cases", title = "Daily new cases and deaths", fill = "") +
  guides(fill = guide_legend(order = 1)) +
  scale_fill_brewer(name = "", palette = "Set2", labels = c("New case", "New death")) +
  scale_color_manual(name = moveAvg %>% as.character() %>% 
                       paste0("-day moving average"), 
                     values = RColorBrewer::brewer.pal(3, "Dark2"), 
                     labels = c("New case", "New death")) +
  scale_x_date(date_breaks = "3 days", date_labels = "%b %d") +
  theme_minimal() #+
 # theme(panel.grid.major.x = element_blank(), 
 #       legend.margin = margin(),
 #       legend.box = "vertical",
 #       legend.position = "bottom", 
 #       axis.text.x = element_text(size = 10, angle = 50, hjust = 1), 
 #       text = element_text(size = 14), 
 #       legend.text = element_text(size = 12))


renderPlot({
  p1
  })


```


```{r plot2, echo=FALSE, warning = FALSE, message=FALSE}

## plots from COVID.R
# df <- dataWide %>% 
#   drop_na(Daily.tests)

# loclevels <- droplevels(df$Date)

SO <- StateOrders %>% 
  filter(state == tabstate) %>%
  select(-state) %>%
  pivot_longer(everything()) %>%
  mutate(value = as.Date(value, "%m - %d - %Y"))


#df <- df %>%
#  select(Date, PositivePercent, DeathPercent, Daily.tests, Date, Daily.tests) 
#
#df$PositivePercent[which(!is.finite(df$PositivePercent))] <- 0

df2 <- dataLongDailyTests %>% 
             filter(Variable %in% c("PositivePercent","DeathPercent")) %>% 
             mutate(Value = Value*100)

ymax <- max(df2$Value[is.finite(df2$Value)])


p2 <- ggplot() +
  geom_col(data = df2, 
           aes(x = Date, y = Value, fill = rev(Variable)), 
           color = NA, 
           position = "dodge", 
           width = .85, 
           alpha = .5) +
  geom_vline(xintercept = SO$value, lty = 2) + 
  geom_path(data = dataLongAvg %>% 
              filter(Variable %in% c("PositivePercent","DeathPercent")), 
            aes(Date, movAvgValue*100, 
                color = rev(Variable), 
                group = Variable), 
            size = 1.8, 
            alpha = .8) +
  #geom_text_repel(data = dataLongDailyTests %>% 
  #                  filter(Variable %in% c("PositivePercent")) %>% 
  #                  filter(Date == last(Date)), 
  #                aes(x = Date, y = Value*100, label = round(Value*100,2)), segment.color = NA, direction = "y", box.padding = .05, nudge_x = -.05, nudge_y = 1, size = 3.5) +
  #geom_text_repel(data = dataLongDailyTests %>% 
  #                  filter(Variable %in% c("DeathPercent")) %>% 
  #                  filter(Date == last(Date)), 
  #                aes(x = Date, y = Value*100, label = round(Value*100,2)), segment.color = NA, direction = "y", box.padding = .05, nudge_x = .5, nudge_y = 1, size = 3.5, ylim = c(0, Inf)) +
  geom_point(inherit.aes = F, data = dataWide, aes(x = Date, y = -1, size = Daily.tests), shape = 21, stroke = 1, fill = "white") +
  scale_color_manual(name = moveAvg %>% 
                       as.character() %>% 
                       paste0("-day moving average"), 
                     values = (RColorBrewer::brewer.pal(3, "Dark2")[1:2]), 
                     label = c("Positive rate", "Fatality rate")) +
    annotate("label", 
           x = SO$value ,
           y = c(ymax * 0.30, ymax * 0.50, ymax * 0.70, ymax * 0.85, ymax * 0.95), 
           label = SO$name) +
   annotate("rect", 
            xmin = as.Date(today(), format = '%d-%B-%Y') - 7, 
            xmax = today(), 
            ymin = 0, 
            ymax = Inf, 
            alpha = .15) +
  labs(x = "", y = "Percentage (%)", title = "Daily positive rate and case fatality rate", size = "Daily tests", fill = "Positive rate") +
  guides(color = guide_legend(nrow = 1, byrow = TRUE, order = 2), size = guide_legend(order = 3), fill = guide_legend(order = 1)) +
  scale_x_date(date_breaks = "3 days", date_labels = "%b %d") +
  scale_fill_manual(name = "", label = c("Positive rate","      Fatality rate \n(total death/total case)"), values = (RColorBrewer::brewer.pal(3, "Set2")[1:2])) +
  scale_size_continuous(range = c(.1,4)) +
  theme_minimal() #+
 #theme(panel.grid.major.x = element_blank(),
 #      legend.margin = margin(),
 #      legend.box = "vertical",
 #      legend.position = "bottom", 
 #      axis.text.x = element_text(size = 10, 
 #                                 angle = 50, 
 #                                 hjust = 1), 
 #      text = element_text(size = 14),
 #      legend.text = element_text(size = 12))
 


renderPlot({
  p2
  })


```

